%-------------------------
% Resume in %-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3.3pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-12pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  {\textbf{\Large Kartik Saxena}} & Email : \href{mailto:cs16mi505@nith.ac.in}{cs16mi505@nith.ac.in}\\
  \href{https://github.com/SaxenaKartik}{github.com/SaxenaKartik} \& \href{https://sourcerer.io/SaxenaKartik}{sourcerer.io/SaxenaKartik}  & Phone No : +91 7982293578\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Bachelor of Computer Science and Engineering;  GPA: 9.11}{Jul. 2016 -- Till Date}
    {National Institute of Technology Hamirpur}{Himachal Pradesh, India}
    % \resumeSubheading
    %   {Delhi Public School Ghaziabad}{Uttar Pradesh, India}
    %   {Senior Secondary School (95\%)}{Jul. 2014 -- Jul. 2016}
    % \resumeSubheading
    %   {St. Mary's Convent School, Ghaziabad}{Uttar Pradesh, India}
    %   {High School (93.4\%)}{}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Mechanical Chef}{}
      {Summer Internship 2019}{May 2019 - July 2019}
      \resumeItemListStart
        \resumeItem{Website and Backend}
          {Built the official mechanical chef website in Django with a MySQL backend, to automate the process of preparing any dish using the Mechanical Chef Robot.}
        \resumeItem{Simulator}
          {Built a state-based simulator using MVC design pattern to test and debug the website. The simulator worked by polling the website for any instructions given by the user.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Memex-Worldbrain}{}
      {Open Source Contribution}{Jan 2019 - May 2019}
      \resumeItemListStart
        \resumeItem{ReactJS}
          {Contributed to Memex by WorldBrain worked at \href{https://github.com/WorldBrain/Memex/pull/739}{\textbf{Overhauling the memex design}} and modularizing the built-in components for quick and easy future implementation.}
        \resumeItem{Solved Bug}
          {Merged a \href{https://github.com/WorldBrain/Memex/pull/693}{\textbf{pull request}} solving a bug in the dashboard of the browser extension}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% -------------------------------------------

% --------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Programming Languages}{: Python3, C++, C, JavaScript, Java}
     % \hfill
   }
   % \item{
   %    \textbf{Technologies}{: ReactJS, NodeJS}
   %    \hfill
   % }
   \item{
      \textbf{Frameworks, Tools and Technologies}{: Django, Django REST Framework, Git, Github, Design Patterns, NodeJS, ReactJS, Selenium Webdriver, PyGame, MATLAB, GNU/Linux, LaTeX, AWS}
   }
 \resumeSubHeadingListEnd


% -------------------------------------------

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Wireless Access Points Through UAVs}
    { To build, deploy and manage a wireless network using UAVs used as wireless access points aimed at providing internet facility to the places that lack proper infrastructure. Built using Django and Django REST Framework with a SQL database.
    }
    \resumeSubItem{Your-Scheduler}
    { A real-time priority based scheduling application, that can build real-time schedule for the everyday activities of a user, ensure that the schedule is customizable by the user and also monitor the efficiency of the user. It is built using Django Framework with a MySQL database. The website is deployed at \href{https://your-scheduler.herokuapp.com}{\textbf{your-scheduler.herokuapp.com}}
    }
    \resumeSubItem{Mechanical Chef Website}
      {An interface between the mechanical chef robot and the user along with backend support to maintain a profile, place orders on the robot, see the realtime status of the dish being prepared with video streaming. Also built a simulator using the MVC design pattern to simulate the state-based actions of the robot.}
    \resumeSubItem{NQUEENS Visualization}
      {A visualization of NQUEENS problem in Python and C++, built using Subprocess python library.}
    \resumeSubItem{Library Management Software}
      {Open source software for the use of a librarian built-in Java Netbeans IDE with a backend in MySQL}
    %\resumeSubItem{Search Engine}
    %  {A search engine built in python as a part of \href{https://classroom.udacity.com/courses/cs101}{\textbf{this}} course on udacity}
  \resumeSubHeadingListEnd


%-----------ACHIEVEMENTS-----------------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem{ACM-ICPC 2019}
      {Member of team RBTREE NODES which got a \href{https://www.codechef.com/public/rankings/ACM18KOL}{\textbf{Rank of 40}} out of 159 participating teams in the Kanpur Regionals of the contest. More than 4000 participants participated in the online round. Received an Honourable Mention amongst the 159 qualifying teams.}
    \resumeSubItem{Snackdown 2019}
      {Member of team RBTREE NODES which got a \href{https://www.codechef.com/rankings/SNCK1B19?order=asc&search=rbtree&sortBy=rank}{\textbf{Global Rank 1}} in the Online Round 1B with over 15856 teams participating}
  \resumeSubHeadingListEnd

%-----------CO-CURRICULAR-----------------
\section{CO-CURRICULAR}
  \resumeSubHeadingListStart
    \resumeSubItem{Joint Secretary App Team NITH}
      {Organizing member of \href{https://www.hackonhills.com/}{\textbf{Hack On Hills}}. Being 2nd most registered student held Hackathon in India with about 1068 registrations on DevFolio after Hack In Out 2019. Backend Developer of various Android Apps built annually for the college fests. Organized various workshops on \textbf{Git \& Github}}
    \resumeSubItem{Senior Executive Member CSEC NITH}
      {Organizing member of CSEC's monthly programming contest \textbf{Heuristics} on hackerearth and codeforces. Conducted weekly programming meets for freshmen}
    \resumeSubItem{Volunteer GLUG NITH}
      {Organizing member of \textbf{Software Freedom Day Celebration} in NITH for four consecutive years, aimed at promoting the use of free and open-source software.}
    \resumeSubItem{Senior Editor Team SRIJAN}
      {Member of \textbf{English Team} in the official college magazine. Written articles on how the coding culture of our college is flourishing and giving rise to startups, hackathons and GSOC representation}
    \resumeSubItem{English Club}
      {Member of \textbf{English Club} in NITH. Organized the first and second iteration of the Annual Literature Fest of our college \textbf{LIT AF} and various other events}
  \resumeSubHeadingListEnd
\end{document}
